Some title

### 2018-01-12 tex/paper.tex
Changes to the paper
Tex

\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings.\footnote{This is an abstract footnote}
\end{abstract}

@@

\caption{An overview of the complete neural network being used. Ocher stands for the input, blue for linear layers, red for LSTM layers, green for linear layers with a softplus activation function and purple for the outputs of the neural network. The numbers in parentheses next to each label stand  for the number of neurons being used in that layer.}
\label{fig:neural_network}
\end{figure}

>>>>

\begin{abstract}
This paper proposes a new method of congestion control in packet-switched networks that uses on-line reinforcement learning to determine the optimum congestion window size at a given point in time with respect to a chosen utility function.

To this end we use an Artifical Neural Network based approach that can be initialized with a previously trained neural network or with random weights (without any preknowledge). When being used without any preknowledge the approach converges to a stable solution within the order of minutes and then outperforms existing congestion control algorithms with respect to throughput.

To our knowledge (\todo{Make sure this is really true!})

\end{abstract}

@@

\caption{An overview of the complete neural network being used. Ocher stands for the input, blue for linear layers, red for LSTM layers, green for linear layers with a softplus activation function and purple for the outputs of the neural network. The numbers in parentheses next to each label stand for the number of width of that layer (i.e.~the number of neurons except for the inputs and outputs).}
\label{fig:neural_network}
\end{figure}
